Legacy Data Confounds Modern Genomics Studies

### 2018-07-31 legacy.tex
Finishing up genome wide run

To identify SNPs that are likely to reproduce poorly across cohorts (without having access to a second cohort), we performed a genome-wide association study (GWAS) in the JPT for SNPs that correlate strongly with low quality \ref{SFS}. 
Using the linear regression as implemented in PLINK, we were able to identify $625$ snips with $p < 10^{-8}$ and $1048$ snps with $ p < 10^{-6}.$ 
While identifying putative low-quality SNPs to exclude, using a higher $p$-value threshold increases the stringency of the filtering (i.e., the traditional genome-wide significance threshold might not be a good guide for filtering).  
 This GWAS included 104 Japanese individuals, \todo{000} of which were sequenced in phase 1 while the rest were sequenced in phase 3 of the 1kGP.
The variants that are associated to the quality of mapped bases have a 10 fold enrichment in *AC${\rightarrow}$*CC mutations.

>>>>

To identify SNPs that are likely to reproduce poorly across cohorts (without having access to a second cohort), we performed a genome-wide association study (GWAS) in the JPT for SNPs that correlate strongly with low quality \ref{SFS}.
\luke{NEW:} 
Whereas the majority of GWAS use linear regression predicting a phenotype based on genotype, our method does the inverse.
We are looking for loci where the genotypes are predictable based on the data quality scores.
We were able to identify \todo{000} SNPs with $p < 10^{-8}$ and \todo{000} SNPs with $ p < 10^{-6}$.
While identifying putative low-quality SNPs to exclude, using a higher $p$-value threshold increases the stringency of the filtering (i.e., the traditional genome-wide significance threshold might not be a good guide for filtering).  
 %This GWAS included 104 Japanese individuals, 74 of which were sequenced in using the Genome Analyzer II while the rest were sequenced using the HiSeq 2000 of the 1kGP.
The variants that are associated to the quality of mapped bases have an enrichment in *AC${\rightarrow}$*CC mutations.
